3D Magnetic modelling of ellipsoidal bodies

### 2017-02-15 manuscript/manuscript.tex
include the relationship between alpha, gamma and delta and strike, dip and rake

Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
$x$, $y$ and $z$ pointing to, respectively, North, East and down.
For convenience, we denominate this coordinate system as 
\textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
Let us consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
orientation defined by angles \textit{strike}, \textit{dip}, and
\textit{rake} (Fig. \ref{fig:orientation-angles}a), and semi-axes defined by
positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
The angles strike, dip and rake are commonly used to
define the orientation of lines in structural geology
\citep{clark1986, allmendinger2012}.

PAREI AQUI

The points $(x, y, z)$ located on the surface of this ellipsoidal body
satisfy the following equation:
\begin{equation}
(\mathbf{r} - \mathbf{r}_c)^T \mathbf{A} (\mathbf{r} - \mathbf{r}_c) = 1 \: ,
\label{eq:ellipsoid_surface}
\end{equation}
where $\mathbf{r} = [\begin{array}{ccc} x & y & z \end{array} ]^{\top}$,
$\mathbf{r}_{c} = [\begin{array}{ccc} x_{c} & y_{c} & z_{c} \end{array} ]^{\top}$,
$\mathbf{A}$ is a positive definite matrix given by
\begin{equation}
\mathbf{A} = \mathbf{V}
\left[ \begin{array}{ccc}
a^{-2} & 0 & 0 \\
0 & b^{-2} & 0 \\
0 & 0 & c^{-2} 
\end{array} \right] \mathbf{V}^{\top} \: ,
\label{eq:A}
\end{equation}
and $\mathbf{V}$ is an orthogonal matrix whose columns are defined
by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$.

The vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ 
depend on the orientation angles 
$\alpha$, $\beta$, $\gamma$ and are defined 
as follows \citep{clark1986}:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v1_triaxial_prolate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\                   
                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\ 
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v2_triaxial_prolate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_triaxial_prolate}
\end{equation}
For triaxial ellipsoids (i.e., $a > b > c$), the orthogonal matrix
$\mathbf{V}$ (Eq. \ref{eq:A}) is calculated by using Eqs.
\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate} as follows:
\begin{equation}
\mathbf{V} = \left[ \begin{array}{ccc}
\mathbf{v}_{1} & \mathbf{v}_{2} & \mathbf{v}_{3}
\end{array} \right] \: .
\label{eq:V_triaxial_prolate}
\end{equation}
Similarly, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
prolate ellipsoids (i.e., $a > b = c$) is calculated according
to Eq. \ref{eq:V_triaxial_prolate} by using Eqs.
\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ 
\citep{emerson1985}.
Finally, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
oblate ellipsoids (i.e., $a < b = c$) is calculated by 
using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
\citep{emerson1985}:
\begin{equation}
\mathbf{V} = \left[ \begin{array}{ccc}
\mathbf{v}_{2} & \mathbf{v}_{1} & -\mathbf{v}_{3}
\end{array} \right] \: .
\label{eq:V_oblate}
\end{equation}
The orientation of the semi-axes $a$, $b$, and $c$ are defined 
by the first, second, and third columns of the matrix 
$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
in the case of a triaxial or prolate ellipsoid, or the
matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
in the case of an oblate ellipsoid.

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to Eqs. \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.
%Similarly, we may properly use the orthogonality of 
%matrix $\mathbf{V}$ to transform a generic 
%linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$,
%referred to the main coordinate system, into a new
%linear system 
%$\tilde{\mathbf{M}} \, \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$,
%referred to a local coordinate system, 
%as follows:
%\begin{equation}
%\underbrace{\mathbf{V}^{\top} \mathbf{M} \mathbf{V}}_{\tilde{\mathbf{M}}} \, 
%\underbrace{\mathbf{V}^{\top} \mathbf{p}}_{\tilde{\mathbf{p}}} = 
%\underbrace{\mathbf{V}^{\top} \mathbf{d}}_{\tilde{\mathbf{d}}} \: .
%\label{eq:matrix-transformation}
%\end{equation}

@@

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
In general, the susceptibility tensor $\mathbf{K}$ is represented,
in the main coordinate system, as follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions} \citep{hrouda1982}.
For the particular case in which the principal directions 
coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
equal to the matrix $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate}
and \ref{eq:V_oblate}), depending on the ellipsoid type.
Another important particular case is that in which the
susceptibility is isotropic and, consequently, the principal
susceptibilities $k_{1}$, $k_{2}$, and $k_{3}$ (Eq. \ref{eq:K})
are equal to a constant $\chi$. In this case, the susceptibility
tensor $\mathbf{K}$ (Eq. \ref{eq:K}) assumes the particular form
\begin{equation}
\mathbf{K} = \chi \, \mathbf{I} \: ,
\label{eq:K-isotropic}
\end{equation}
where $\mathbf{I}$ represents the identity matrix.

@@

The following part of this paper moves on to describe 
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) at points located
both within and without the volume $\vartheta$ of the ellipsoidal
body. However, the mathematical developments are conveniently 
performed in the local coordinate system related to the
respective ellipsoidal body.

@@

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system.
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
macmillan1958, lowes1974,  peake1953, chang1961, clark1986, 
tejedor1995, sttraton2007}.

@@

The second important coordinate transformation is defined
with respect to Eq. \ref{eq:H-M-uniform}.
By properly using the orthogonality of matrix $\mathbf{V}$ 
(Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) can be transformed
from the main coordinate system to a local coordinate system
as follows:
\begin{equation}
\underbrace{\mathbf{V}^{\top} \mathbf{H}(\mathbf{r})}_{\tilde{\mathbf{H}}(\tilde{\mathbf{r}})} = 
\underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
- \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
_{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
\underbrace{\mathbf{V}^{\top} \mathbf{K} \mathbf{V}}
_{\tilde{\mathbf{K}}} \; 
\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\dagger}}
_{\tilde{\mathbf{H}}^{\dagger}} \: ,
\label{eq:H-tilde}
\end{equation}
where the superscript "$\sim$" denotes quantities
referred to the respective local coordinate system.

In Eq. \ref{eq:H-tilde}, the transformed
depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
is calculated as a function of the original depolarization
tensor $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform}).
In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
are calculated as a function of the second derivatives of the
function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
which is defined in the main coordinate system.
It can be shown (Appendix A), however, that the
elements $\tilde{n}_{ij}(\tilde{\mathbf{r}})$ of
$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ can also be calculated
as follows:
\begin{equation}
\tilde{n}_{ij}(\tilde{\mathbf{r}}) = - 
\frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}} 
\: , \quad i = 1, 2, 3 \: , \quad j = 1, 2, 3 \: ,
\label{eq:nij-tilde}
\end{equation}
where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, 
and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Eq. \ref{eq:fi-tilde}
or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
point located within or without the volume $\vartheta$ of the
ellipsoidal body.

@@

For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
can be rewritten as follows:
\begin{equation}
\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
0 & 0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
\end{array} \right] \left( \chi \, \tilde{\mathbf{H}}_{0} +
\tilde{\mathbf{M}}_{R} \right) \: .
\label{eq:M-tilde-K-isotropic}
\end{equation}
This equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\tilde{\mathbf{H}}_{0}$, 
represents the induced magnetization whereas the term depending on
$\tilde{\mathbf{M}}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-tilde-K-isotropic} reveals that, as pointed out by \citet{maxwell1873},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-KH}), defined in the main coordinate system,
can be approximated as follows:
\begin{equation}
\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$,
whether it is parallel to an ellipsoid axis or not.

@@

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar
function obtained by transforming $f(\mathbf{r})$ 
(Eq. \ref{eq:f}) from the
main coordinate system to a local coordinate system.
For convenience, let us rewrite Eq. 
\ref{eq:coord_transformation} as follows:
\begin{equation}
\tilde{r}_{k} = v_{k1} \, r_{1} + v_{k2} \, r_{2} + v_{k3} \, r_{3} + c_{k} \: ,
\label{eq:r-tilde-k}
\end{equation}
where $\tilde{r}_{k}$, $k = 1, 2, 3$, are the elements of the transformed
position vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}),
$r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
$\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
$v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
$\mathbf{V}$ (Eq. \ref{eq:V_triaxial_prolate} or \ref{eq:V_oblate}),
and $c_{k}$ is a constant defined by the coordinates
$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoidal body.

>>>>

Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
$x$, $y$ and $z$ pointing to, respectively, North, East and down.
For convenience, we denominate this coordinate system as 
\textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
Let us consider an ellipsoidal body with centre at the point 
$(x_{c}, y_{c}, z_{c})$, orientation defined by three angles 
$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a), 
and semi-axes defined by
positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
The angles $\varepsilon$, $\zeta$, and $\eta$ are called \textit{strike}, 
\textit{dip}, and \textit{rake}, respectively, and are commonly used to
define the orientation of lines in structural geology
\citep{clark1986, allmendinger2012}.
The points $(x, y, z)$ located on the surface of this ellipsoidal body
satisfy the following equation:
\begin{equation}
(\mathbf{r} - \mathbf{r}_c)^T \mathbf{A} (\mathbf{r} - \mathbf{r}_c) = 1 \: ,
\label{eq:ellipsoid_surface}
\end{equation}
where $\mathbf{r} = [\begin{array}{ccc} x & y & z \end{array} ]^{\top}$,
$\mathbf{r}_{c} = [\begin{array}{ccc} x_{c} & y_{c} & z_{c} \end{array} ]^{\top}$,
$\mathbf{A}$ is a positive definite matrix given by
\begin{equation}
\mathbf{A} = \mathbf{V}
\left[ \begin{array}{ccc}
a^{-2} & 0 & 0 \\
0 & b^{-2} & 0 \\
0 & 0 & c^{-2} 
\end{array} \right] \mathbf{V}^{\top} \: ,
\label{eq:A}
\end{equation}
and $\mathbf{V}$ is an orthogonal matrix whose first, second and third columns 
are defined by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
(Fig. \ref{fig:orientation-angles}b), respectively, depending on the ellipsoid type.
These unit vectors depend on orientation angles $\alpha$, 
$\beta$, and $\gamma$, which are not commonly used in
geosciences. These angles, however, can be defined from
$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a)
as follows \citep{clark1986}:
\begin{equation}
\alpha = \varepsilon - \cos^{-1} \left[ \frac{\cos \eta}
{\left( 1 - \sin^{2} \zeta \, \sin^{2} \eta \right)^{\frac{1}{2}}}\right] \: ,
\label{eq:alpha}
\end{equation}
\begin{equation}
\gamma = \tan^{-1} \left( \frac{\cos \zeta}{\sin \zeta \, \cos \eta}\right)
\label{eq:gamma}
\end{equation}
and
\begin{equation}
\delta = \sin^{-1} \left( \sin \zeta \, \sin \eta \right) \: ,
\label{eq:delta}
\end{equation}
where $-90^{\circ} \leq \gamma \leq 90^{\circ}$ and
$0 \leq \delta \leq 90^{\circ}$.
Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a and Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}), we define the unit vectors
$\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
(Fig. \ref{fig:orientation-angles}b) according to the ellipsoid type.
For triaxial ellipsoids (i.e., $a > b > c$), these unit vectors are 
given by \citep{clark1986}:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v1_triaxial_prolate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\                   
                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\ 
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v2_triaxial_prolate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_triaxial_prolate}
\end{equation}
Similarly, the unit vectors defining the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
prolate ellipsoids (i.e., $a > b = c$) are calculated
by using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$
\citep{emerson1985}.
Finally, the unit vectors defining the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \sin\gamma \; \sin\delta + \sin\alpha \; \cos\gamma \\               
                  -\sin\alpha \; \sin\gamma \; \sin\delta - \cos\alpha \; \cos\gamma \\ 
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v1_oblate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v2_oblate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \sin\gamma + \cos\alpha \; \cos\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \sin\gamma + \sin\alpha \; \cos\gamma \; \sin\delta \\
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_oblate}
\end{equation}
These formulas are similar to those presented by \citep{emerson1985}.

%The orientation of the semi-axes $a$, $b$, and $c$ are defined 
%by the first, second, and third columns of the matrix 
%$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
%in the case of a triaxial or prolate ellipsoid, or the
%matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
%in the case of an oblate ellipsoid.
The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre
(Fig. \ref{fig:orientation-angles}b).
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
(Eq. \ref{eq:A}) is defined according to the ellipsoid type.

@@

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
In general, the susceptibility tensor $\mathbf{K}$ is represented,
in the main coordinate system (Fig. \ref{fig:orientation-angles}a), as follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions} \citep{hrouda1982}.
For the particular case in which the principal directions 
coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
equal to the matrix $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate}
and \ref{eq:V_oblate}), depending on the ellipsoid type.
Another important particular case is that in which the
susceptibility is isotropic and, consequently, the principal
susceptibilities $k_{1}$, $k_{2}$, and $k_{3}$ (Eq. \ref{eq:K})
are equal to a constant $\chi$. In this case, the susceptibility
tensor $\mathbf{K}$ (Eq. \ref{eq:K}) assumes the particular form
\begin{equation}
\mathbf{K} = \chi \, \mathbf{I} \: ,
\label{eq:K-isotropic}
\end{equation}
where $\mathbf{I}$ represents the identity matrix.

@@

The following part of this paper moves on to describe 
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) at points located
both within and without the volume $\vartheta$ of the ellipsoidal
body. However, the mathematical developments are conveniently 
performed in the local coordinate system (Fig. \ref{fig:orientation-angles}b)
related to the respective ellipsoidal body.

@@

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system (Fig. \ref{fig:orientation-angles}a)
into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system (Fig. \ref{fig:orientation-angles}b).
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
macmillan1958, lowes1974,  peake1953, chang1961, clark1986, 
tejedor1995, sttraton2007}.

@@

The second important coordinate transformation is defined
with respect to Eq. \ref{eq:H-M-uniform}.
By properly using the orthogonality of matrix $\mathbf{V}$ 
(Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) can be transformed
from the main coordinate system (Fig. \ref{fig:orientation-angles}a) 
to the local coordinate system (Fig. \ref{fig:orientation-angles}b) as follows:
\begin{equation}
\underbrace{\mathbf{V}^{\top} \mathbf{H}(\mathbf{r})}_{\tilde{\mathbf{H}}(\tilde{\mathbf{r}})} = 
\underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
- \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
_{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
\underbrace{\mathbf{V}^{\top} \mathbf{K} \mathbf{V}}
_{\tilde{\mathbf{K}}} \; 
\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\dagger}}
_{\tilde{\mathbf{H}}^{\dagger}} \: ,
\label{eq:H-tilde}
\end{equation}
where the superscript "$\sim$" denotes quantities
referred to the respective local coordinate system.

In Eq. \ref{eq:H-tilde}, the transformed
depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
is calculated as a function of the original depolarization
tensor $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform}).
In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
are calculated as a function of the second derivatives of the
function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
which is defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a).
It can be shown (Appendix A), however, that the
elements $\tilde{n}_{ij}(\tilde{\mathbf{r}})$ of
$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ can also be calculated
as follows:
\begin{equation}
\tilde{n}_{ij}(\tilde{\mathbf{r}}) = - 
\frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}} 
\: , \quad i = 1, 2, 3 \: , \quad j = 1, 2, 3 \: ,
\label{eq:nij-tilde}
\end{equation}
where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, 
and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Eq. \ref{eq:fi-tilde}
or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
point located within or without the volume $\vartheta$ of the
ellipsoidal body.

@@

For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
can be rewritten as follows:
\begin{equation}
\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
0 & 0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
\end{array} \right] \left( \chi \, \tilde{\mathbf{H}}_{0} +
\tilde{\mathbf{M}}_{R} \right) \: .
\label{eq:M-tilde-K-isotropic}
\end{equation}
This equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\tilde{\mathbf{H}}_{0}$, 
represents the induced magnetization whereas the term depending on
$\tilde{\mathbf{M}}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-tilde-K-isotropic} reveals that, as pointed out by \citet{maxwell1873},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-KH}), defined in the main coordinate system
(Fig. \ref{fig:orientation-angles}a),
can be approximated as follows:
\begin{equation}
\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$,
whether it is parallel to an ellipsoid axis or not.

@@

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar
function obtained by transforming $f(\mathbf{r})$ 
(Eq. \ref{eq:f}) from the
main coordinate system (Fig. \ref{fig:orientation-angles}a)
to the local coordinate system (Fig. \ref{fig:orientation-angles}b).
For convenience, let us rewrite Eq. 
\ref{eq:coord_transformation} as follows:
\begin{equation}
\tilde{r}_{k} = v_{k1} \, r_{1} + v_{k2} \, r_{2} + v_{k3} \, r_{3} + c_{k} \: ,
\label{eq:r-tilde-k}
\end{equation}
where $\tilde{r}_{k}$, $k = 1, 2, 3$, are the elements of the transformed
position vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}),
$r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
$\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
$v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
$\mathbf{V}$ (Eq. \ref{eq:V_triaxial_prolate} or \ref{eq:V_oblate}),
and $c_{k}$ is a constant defined by the coordinates
$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoidal body.
